---
title: "Cleaning Template"
author: "Chayce Baldwin"
date: "7/24/2020"
output: 
    html_document:
    toc: TRUE
    toc_float: TRUE
    number_sections: TRUE
---

```{r clean system, message=TRUE, warning=TRUE, include=FALSE}
rm(list = ls()) # clean environment

#options(knitr.table.format = "word_document")

knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```

```{r include = FALSE}
# install.packages("package_name")

library(devtools)
library(knitr)
library(tidyverse)
library(kableExtra)
library(magrittr)
library(Hmisc)
library(psych)
library(haven)
library(dplyr)
install_github("crbwin/clnR")
library(clnR2)
```

# Load and tidy data

```{r loading data}
gr <- read.csv("../Data/<filename>_ready.csv", header = TRUE)

d <- read.csv("C:\\Users\\cbwin\\Dropbox (Character Lab)\\Grit Rubric Project\\Data\\Grit+Rubric_July+16+2020_13.08_ready_SATACT.csv", header = TRUE)
```


```{r}
# get rid of outliers of time took, or less than a time that you think it should have taken (e.g. get rid of 5 min or less)

d %<>% dplyr::filter(att_check==20)

d %<>% dplyr::filter(DistributionChannel!="preview")

d %<>% rename(duration = `Duration..in.seconds.`)


time.tab <- d %>% select(duration) %>% 
                      mutate(
                         duration_min = duration/60,
                         duration_z = scale(duration)
                            ) %>% 
                    dplyr::filter(duration_z > -3.29) %>%  #& duration_z < 3.29) %>% 
                    psych::describe() # n = 

time.tab

d %>% filter(duration < (median(duration)/2)) %>% select(duration) # n = 6

d %<>% filter(duration > (median(duration)/2))


```

```{r}
d %<>% select(
  
  ## Grit rubric
  gr_pass = gr_pass_1, 
  gr_pers = gr_pers_1,
  
  ## Grit-12
  grit1:grit12,
  
  ## Self-control (BSCS)
  sc1:sc13,
  
  ## Deomgraphics
  birthyr = birthyr_1,
  gender,
  
  white,
  amindian,
  black,
  asian,
  hispanic,
  pacisl,
  multirace,
  
  educ, 
  income
  
)
```

## Demographics

```{r}
# if race vars in data are separate columns
cwb %<>% 
  mutate(
    race = case_when(
 white == 1 ~ "White",
 amindian == 1 ~ "Native Am.",
 black == 1 ~ "Black",
 asian == 1 ~ "Asian",
 hispanic == 1 ~ "Latinx",
 pacisl == 1 ~ "Pac. Islander",
 multirace == 1 ~ "Multirace",
 TRUE ~ NA_character_
    )
  )

cwb %<>% mutate(
  race_f <- factor(race, levels=unique(race)),
  female_f <- factor(gender, levels = c(0, 1), labels = c("Male", "Female"))
)


##if age is input as birth year

#educ coding

#income coding






```

checking distributions of demographics
```{r}

```


Copy in the notes that Juan had above composite creation
do the code for the demographics, add some common ones

# Creating composites

## Grit

### Overall

*Note*:

#### Recoding and grouping quosures
```{r}
d %<>% mutate(
  grit2_r = 6 - grit2,
  grit3_r = 6 - grit3,
  grit5_r = 6 - grit5,
  grit7_r = 6 - grit7,
  grit8_r = 6 - grit8,
  grit11_r = 6 - grit11
)

q_grit <- quos(grit1, grit2_r, grit3_r, grit4, grit5_r, grit6, grit7_r, grit8_r, grit9, grit10, grit11_r, grit12)
```

#### Summarizing
```{r}
d %>% table.describe(q_grit)
d %>% table.freq(q_grit)
```

#### Reliability
```{r}
d %>% alphatize(q_grit, neg.corr = FALSE) ## a = .91

table.corr(gr, q_grit)
```

#### Factor Analysis
```{r}
d %>% factorize(q_grit, factors = 2)
```

#### Compute Composite
```{r}
d %<>% cv_bake(grit, q_grit)
```

#### Describe
```{r}
  hist(d$grit)
  boxplot(d$grit)
```

### Passion

*Note*:

#### Recoding and grouping quosures
```{r}
q_grit_pass <- quos(grit2_r, grit3_r, grit5_r, grit7_r, grit8_r, grit11_r)

```

#### Summarizing
```{r}
d %>% table.describe(q_grit_pass)
d %>% table.freq(q_grit_pass)
```

#### Reliability
```{r}
d %>% alphatize(q_grit_pass, neg.corr = FALSE) ## a = .91

table.corr(gr, q_grit_pass)
```

#### Factor Analysis
```{r}
d %>% factorize(q_grit_pass, factors = 1)
```

#### Compute Composite
```{r}
d %<>% cv_bake(grit_pass, q_grit_pass)
```

#### Describe
```{r}
  hist(d$grit_pass)
  boxplot(d$grit_pass)
```

### Perseverance

*Note*:

#### Recoding and grouping quosures
```{r}
q_grit_pers <- quos(grit1, grit4, grit6, grit9, grit10, grit12)
```

#### Summarizing
```{r}
d %>% table.describe(q_grit_pers)
d %>% table.freq(q_grit_pers)
```

#### Reliability
```{r}
d %>% alphatize(q_grit_pers, neg.corr = FALSE) ## a = .82

table.corr(gr, q_grit_pers)
```

#### Factor Analysis
```{r}
d %>% factorize(q_grit_pers, factors = 1)
```

#### Compute Composite
```{r}
d %<>% cv_bake(grit_pers, q_grit_pers)
```

#### Describe
```{r}
  hist(d$grit_pers)
  boxplot(d$grit_pers)
```

## self-control

*Note*:

### Recoding and grouping quosures
```{r}

d %<>% 
  mutate(
    sc2_r = 6 - sc2,
    sc3_r = 6 - sc3,
    sc4_r = 6 - sc4,
    sc5_r = 6 - sc5,
    sc7_r = 6 - sc7,
    sc9_r = 6 - sc9,
    sc10_r = 6 - sc10,
    sc12_r = 6 - sc12,
    sc13_r = 6 - sc13
)

q_sc <- quos(sc1, sc2_r, sc3_r, sc4_r, sc5_r, sc6, sc7_r, sc8, sc9_r, sc10_r, sc11, sc12_r, sc13_r)

```

#### Summarizing
```{r}
d %>% table.describe(q_sc)
d %>% table.freq(q_sc)
```

### Reliability
```{r}
d %>% alphatize(q_sc, neg.corr = FALSE) ## a = 0.89
d %>% table.corr(q_sc)
```

### Factor Analysis
```{r}
d %>% factorize(q_sc, factors = 1)
```

### Compute Composite
```{r}
d %<>% cv_bake(sc, q_sc)
```

### Describe
```{r}
  hist(d$sc)
  boxplot(d$sc)
```

# Descriptives and correlations

```{r}
q_all <- quos(grit, grit_pass, grit_pers,
              sc,
              age, female_f, race_f,
              educ, income)
```


```{r}
d %>% table.describe(q_all, alpha = TRUE)
d %>% table.corr(q_all)
```


# Write new data

```{r}
write_rds("../Data/cleaned_<projectname>.rds")
```
---


